Quantitative Benchmarking for Automatically Generated Conjectures

### 2018-02-26 TEBenchmarkPaper/article.tex
Use lists to demonstrate TIP

TIP datatypes can have several ``constructors'' and ``destructors''. For example
the natural numbers can be defined as follows:

\begin{verbatim}
(declare-datatypes () ((Nat (Z) (S (p Nat)))))
\end{verbatim}

This defines the type \texttt{Nat}, along with the constructors \texttt{Z} (for
zero) and \texttt{S} (the successor function), and destructor \texttt{p} (the
predecessor function).

Since our GHC plugin doesn't list constructors or destructors, we add separate
function definitions for each (these are just $\eta$-expansions).

TIP has ``native'' support for booleans and integers, allowing functions like
\texttt{+} to be used without an accompanying definition. Without a definition
these functions will not be included in the QuickSpec exploration, so we replace
all occurrences with custom definitions.

This gives us 3598 definitions in total, with 269 remaining after
$\alpha$-equivalent duplicates are removed.

>>>>

TIP datatypes can have several ``constructors'' and ``destructors''. For example
the type of lists from figure~\ref{figure:list_theory} can be defined in TIP as
follows:

\begin{verbatim}
(declare-datatypes (a) ((List (Nil) (Cons (head a) (tail (List a))))))
\end{verbatim}

This defines a type \texttt{List} parameterised by a type variable \texttt{a}
(the type of the list's elements), with constructors \texttt{Nil} and
\texttt{Cons}, and destructors \texttt{head} and \texttt{tail}. Target languages
(e.g. Haskell and Isabelle) handle constructors and destructors differently, so
we avoid exploring them directly. Rather, we $\eta$-expand each constructor and
destructor to create new function definitions, and rewrite the TIP theorems to
reference these expanded forms instead.

TIP has ``native'' support for booleans and integers, allowing functions like
\texttt{+} to be used without an accompanying definition. To ensure consistency
in the translations, we replace all occurrences of these ``native'' expressions
with standard definitions using the same \texttt{declare-datatypes} and
\texttt{define-fun} mechanisms as the problem set.

This gives us a total of 3598 definitions, including those from the problem set
and our automatically-generated additions. Removing $\alpha$-equivalent
duplicates leaves 269 definitions, and we chose to only sample from those 182
which occur in at least one theorem statement (this removes ambiguity about
which \emph{definitions}, including our generated ones, are ``interesting'' and
which are just ``implementation details'').
